Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-09 paper.tex
add additional paragraphs in governance

\begin{enumerate}
  \item Piracy allows equal access to information
  \item \textcquote{barlow:wine}{I am not comfortable with a model which will restrict inquiry to the wealthy.}

  \item Increased prices are an artificial barrier to access certain
    information. Piracy provides a circumvention to said artificial barrier.
    Piracy gives consumers a way to fight systems they see as
    unfair/censorship. Piracy is a tool of the consumer to control/balance the
    economy~\cite{darnton:pirating-and-publishing, bohannon:everyone}

  \item People pirate medical content.~\cite{till:medical-literature}
    Medical information is valuable to everyone. Having medical information is
    crucial to advancements in medicine, but sometimes the cost is too high.
    The paywalls, in this case, are directly harmful to ends that are
    beneficial to everyone.
\end{enumerate}

\subsection{Governance}

>>>>

\subsection{Governance}
Given that piracy is an illegal usage of another person's conception, it has much to say
in the way of governance and intellectual property laws. The tools of piracy provide the
means of subverting an oppressive regime and call into question the legitimacy of
intellectual property laws.

Having a very firm grip on what citizens can see on the internet is one of the key
characteristics of a despotic government. Such governments know that if they can control
the flow of information on the Internet, it becomes much easier to keep the populace under
control. The government's imposing of restrictions on the Internet is clearly seen when
\textcquote{current:jigsaw} {Tunisia significantly ramped up its already aggressive
blocking of specific websites in response to unrest that would ultimately unseat its
government.} Even more extreme is when governments shutdown the internet entirely to
quickly cease the spread of information. This is exactly what happened on January 28, 2011
in Egypt: \textcquote{current:jigsaw} {Almost simultaneously, about 3,500 individual
Border Gateway Protocol routes [...] were withdrawn on orders from the Egyptian
government, cutting the country off from the rest of the world and bringing internal
communication to a halt.} Fortunately, as already mentioned earlier, piracy excels at
spreading information even when there are those that do not want it spread. BitTorrent is
a peer-to-peer file sharing protocol that is often used when pirating content on the
Internet. A peer-to-peer protocol, by its very nature, does not require a centralized
server to store all the files that are to be shared. Instead, the source of the file is
each person who has the file downloaded. What this means for those under the rule of an
oppressive government is that they can spread information to others in such a way that the
government cannot easily block its source. Pieces of the information are sent to the one
downloading the file from everyone who had the file. There is no single source of the
information that the government can block to stop the spread. By a similar token, there
are peer-to-peer instant messaging applications that do not require an internet connection
to function; you need only be in the vicinity of other people that the message can hop
through to get to the destination. Both of these tools, in the context of piracy, facilitate
the illegal spread of information, but in the context of a despotic government, can be
employed to subvert their attempts at quelling the dispersal of information that could be
harmful to their rule.

Regarding piracy and intellectual property laws, it is clear that the two are at odds with
one another. That being said, it is worth examining whether IP laws accomplish what they
seek to do: encourage innovation. Mark Lemley presents an argument against IP laws when he
writes, \blockcquote[1339]{lemley:faith-based}{[IP] intervenes in the market to interfere
with the freedom of others to do what they want in hopes of achieving the end of
encouraging creativity. If we take that purpose out of the equation, we are left with a
belief system that says the government should restrict your speech and freedom of action
in favor of mine, not because doing so will improve the world, but simply because I spoke
first.} 
To put it differently, intellectual property laws are based on the assumption that in
restricting who is allowed to have certain information, they are encouraging creativity
when, in reality, creativity does not always come first. IP laws are supposed to make
people want to work hard to get a good idea that they can have exclusive ownership of, but
having exclusive rights to an idea stifles further innovation. Under this system, only the
owner has the right to make changes. In fact, it seems that there would be more creativity
without IP laws. If everything was open to scrutiny and replication, there is bound to be
some improvement eventually because of all the people that could have a hand in making it
better. If a big streaming platform were to forfeit one of their IPs to the public, there
is no telling what kind of content could be created. In this way, piracy could allow for
the incremental improvement and scrutiny of conceptions, thus making them better.
